---
title: "Code 1: import data files"
subtitle: "CIES 2021: not everyone has the chance"
author: "dacarras"
date: 'April 29th, 2021'
output:
  html_document:
    theme: paper
    highlight: kate
    number_sections: true
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    fig_width: 10 
    fig_height: 8 
---

<style>
  .main-container {
    max-width: 1600px !important;
  }
  .list-group-item.active, 
  .list-group-item.active:focus, 
  .list-group-item.active:hover {
    background-color: #373334;
  }
</style>



```{r setup, include=FALSE}
#------------------------------------------------------------------------------
# setup
#------------------------------------------------------------------------------

# knitr option
knitr::opts_chunk$set(dev = 'png')
options(knitr.kable.NA = '', digits = 2)

# set appropiate time zone via OlsonNames()
Sys.setenv(TZ="America/Santiago")
Sys.getenv("TZ")
Sys.time()

# fonts
Sys.setenv(LANG="en_US.UTF-8")

# load main library
library(dplyr)


# ---------------------------------------------------------
# get times
# ---------------------------------------------------------

start_time <- Sys.time()

```


# Libraries

## What libraries are used in the present code

```{r , echo=TRUE, warning=FALSE, eval = FALSE}

#------------------------------------------------------------------------------
# libraries
#------------------------------------------------------------------------------

# ---------------------------------------------------------
# libraries for this code
# ---------------------------------------------------------

install.packages('tidyverse')
# many libraries for data management

install.packages('haven')     
# library to open SPSS, STATA, and SAS files
install.packages('devtools')  
# to install developmental libraries

devtools::install_github("dacarras/r4sda") 
# experimental library for analysis of secondary data

```



# File Locations

## Folders

```{r , echo=TRUE, warning=FALSE}

#------------------------------------------------------------------------------
# folders
#------------------------------------------------------------------------------

# ---------------------------------------------------------
# get local path from relative path
# ---------------------------------------------------------

local_path <- function(x){
paste0(tools::file_path_as_absolute('..'),x)
}

# Note: set current directory as working directory
#       e.g. `setwd("/Users/d/cies_2021_opd/01_syntax/")`
#       When a rmd file is run in Rstudio, current directory
#       is the working directory.

# ---------------------------------------------------------
# relative position of folders
# ---------------------------------------------------------

# 00_data
# 01_syntax
# 02_mplus
# 03_figures

# ---------------------------------------------------------
# folder with data files
# ---------------------------------------------------------

data_folder      <- local_path('/00_data/')
syntax_folder    <- local_path('/01_syntax/')
plot_folder      <- local_path('/02_figures/')

# ---------------------------------------------------------
# load main library
# ---------------------------------------------------------

library(dplyr)

# ---------------------------------------------------------
# check folder
# ---------------------------------------------------------

list.files(data_folder)

```


# Problem 1: Import data

- ICCS 2016 public data files consist of a list of 139 different files.
- If we import each of this files one by one, it can be cumbersome, and take a considerable amount of time.
- One way to solve this problem is to use a function that can be repeated many times for each file, and then deliver a single data frame.

## Code 01: import all files and merge these

- To solve the first problem, we will use different libraries to avoid writing an importation code per each file.
- `library(purrr)` has such a function `purrr::map_df()`
- The sequence of the present code is the following:
  + We first get the full list of files that contain students responses.
  + All files starting with the *ISG* letters are the responses to the students questionnaires (see Köhler et al, 2018, p24). Additionally, files ending in "C3" are from ICCS 2016, and ending on "C2" are from ICCS 2009.
  + Once we have a list of the files, we can submit this list to `purrr::map_df()`
  + Within this latter function, we incude `haven::read_sav`, which will read all the SPSS files
  + Afterwards, `purrr::map_df()` will collapse all the imported files into a single data frame
  + Finally, we inspect the generated data file with `dplyr::glimpse()` so we can have a visual proof that the functions is doing what we expect.

```{r, echo=TRUE}

# -----------------------------------------------------------------------------
# import all data
# -----------------------------------------------------------------------------

# -----------------------------------------------
# get list of files
# -----------------------------------------------

iccs_2009_files <- paste0(data_folder, list.files(path = data_folder, pattern = "C2.*"))
iccs_2016_files <- paste0(data_folder, list.files(path = data_folder, pattern = "C3.*"))

# -----------------------------------------------
# import all and merge
# -----------------------------------------------

library(dplyr)
iccs_2009 <- iccs_2009_files %>% 
             purrr::map_df(haven::read_sav)

library(dplyr)
iccs_2016 <- iccs_2016_files %>% 
             purrr::map_df(haven::read_sav)

```

# Problem 2: content of files

- Once data is imported is difficult to know what is its content, unless we read the data file.
- A simple solution, is to accompany the generated data file with a codebook.
- Codebooks are files that contains information regarding what is the content of each variable

## Code 02: Create simple codebook

- The following reads the data frame, and if this is a labelled data frame, it will create a table
- This table has four pieces of information
  + **variable**: the name of the colunm in the data frame
  + **type**: the type of variable (e.g. numeric, character, integer)
  + **values**: a sample of stored values of the vector (i.e. the column in the data frame)
  + **labels**: a description of the variable

```{r, echo=TRUE}

# -----------------------------------------------------------------------------
# create simple codebook
# -----------------------------------------------------------------------------

# -----------------------------------------------
# display variables labels
# -----------------------------------------------

r4sda::variables_table(iccs_2009) %>%
knitr::kable()

# -----------------------------------------------
# save variables table
# -----------------------------------------------

r4sda::variables_table(iccs_2009) %>%
openxlsx::write.xlsx(., paste0(data_folder,'iccs_2009_stu_int_codebook.xlsx'))



# -----------------------------------------------
# display variables labels
# -----------------------------------------------

r4sda::variables_table(iccs_2016) %>%
knitr::kable()

# -----------------------------------------------
# save variables table
# -----------------------------------------------

r4sda::variables_table(iccs_2016) %>%
openxlsx::write.xlsx(., paste0(data_folder,'iccs_2016_stu_int_codebook.xlsx'))

```


# Save data

## Save data to RDS

```{r, echo=TRUE}

# -----------------------------------------------------------------------------
# save data to RDS
# -----------------------------------------------------------------------------

# -----------------------------------------------
# save ICCS 2009
# -----------------------------------------------

saveRDS(iccs_2009, paste0(data_folder,'iccs_2009_stu_int.rds'))

# -----------------------------------------------
# save ICCS 2016
# -----------------------------------------------

saveRDS(iccs_2016, paste0(data_folder,'iccs_2016_stu_int.rds'))

```


# References

Köhler, H., Weber, S., Brese, F., Schulz, W., & Carstens, R. (2018). ICCS 2016 User Guide for the International Database (H. Köhler, S. Weber, F. Brese, W. Schulz, & R. Carstens (eds.)). International Association for the Evaluation of Educational Achievement (IEA).

# Estimated times

```{r , echo=FALSE, include=FALSE}

# ---------------------------------------- 
# estimated times
# ---------------------------------------- 

# get current time
end_time <- Sys.time()

# create table
time_table <- data.frame(
  events = c('start', 'end'),
  times = c(start_time, end_time)
  )

# display time
knitr::kable(time_table, align = 'r') 

```



```{r , echo=TRUE}

# ---------------------------------------- 
# estimated times
# ---------------------------------------- 

difftime(end_time, start_time, units="mins")


```


