---
title: "Code 2: prepare data"
subtitle: "CIES 2021: not everyone has the chance"
author: "dacarras"
date: 'April 29th, 2021'
output:
  html_document:
    theme: paper
    highlight: kate
    number_sections: true
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    fig_width: 10 
    fig_height: 8 
---

<style>
  .main-container {
    max-width: 1600px !important;
  }
  .list-group-item.active, 
  .list-group-item.active:focus, 
  .list-group-item.active:hover {
    background-color: #373334;
  }
</style>



```{r setup, include=FALSE}
#------------------------------------------------------------------------------
# setup
#------------------------------------------------------------------------------

# knitr option
knitr::opts_chunk$set(dev = 'png')
options(knitr.kable.NA = '', digits = 2)


# set appropiate time zone via OlsonNames()
Sys.setenv(TZ="America/Santiago")
Sys.getenv("TZ")
Sys.time()

# fonts
Sys.setenv(LANG="en_US.UTF-8")

# load main library
library(dplyr)


# ---------------------------------------------------------
# get times
# ---------------------------------------------------------

start_time <- Sys.time()

```


# Libraries

## What libraries are used in the present code

```{r , echo=TRUE, warning=FALSE, eval = FALSE}

#------------------------------------------------------------------------------
# libraries
#------------------------------------------------------------------------------

# ---------------------------------------------------------
# libraries for this code
# ---------------------------------------------------------

install.packages('tidyverse')
# many libraries for data management

install.packages('haven')     
# library to open SPSS, STATA, and SAS files

install.packages('labelled')     
# library to add variable labels to data frames

install.packages('devtools')  
# to install developmental libraries

devtools::install_github("dacarras/r4sda") 
# experimental library for analysis of secondary data

```



# File Locations

## Folders

```{r , echo=TRUE, warning=FALSE}

#------------------------------------------------------------------------------
# folders
#------------------------------------------------------------------------------

# ---------------------------------------------------------
# get local path from relative path
# ---------------------------------------------------------

local_path <- function(x){
paste0(tools::file_path_as_absolute('..'),x)  
}

# Note: set current directory as working directory
#       e.g. `setwd("/Users/d/cies_2021_opd/01_syntax/")`
#       When a rmd file is run in Rstudio, current directory
#       is the working directory.


# ---------------------------------------------------------
# relative position of folders
# ---------------------------------------------------------

# 00_data
# 01_syntax
# 02_mplus
# 03_figures

# ---------------------------------------------------------
# folder with data files
# ---------------------------------------------------------

data_folder      <- local_path('/00_data/')
syntax_folder    <- local_path('/01_syntax/')
plot_folder      <- local_path('/03_figures/')

# ---------------------------------------------------------
# load main library
# ---------------------------------------------------------

library(dplyr)

# ---------------------------------------------------------
# check folder
# ---------------------------------------------------------

list.files(data_folder)

```



# Problem 3: survey design variables

- ILSA studies include different variables to express the survey design
- These variables need to be treated to enable modelling of multiple country data frames.

## Code 03: survey design variables

- The present code generates clustering variables that are unique across countries
- Additionally, it creates scaled up survey weights:
  + senate weights scaled up to a 1000
  + within and between school weights for pseudo maximum likelihood estimation of multilevel models, that make use of the survey design.


```{r, echo=TRUE}

# -----------------------------------------------------------------------------
# survey design variables
# -----------------------------------------------------------------------------

# -----------------------------------------------
# load data
# -----------------------------------------------

data_09 <- readRDS(paste0(data_folder, 'iccs_2009_stu_int.rds'))

# -----------------------------------------------
# generic survey design variables
# -----------------------------------------------

library(dplyr)
data_model_09 <- data_09 %>%
                 # remove labels
                 r4sda::remove_labels() %>%
                 # clustering
                 mutate(id_i = seq(1:nrow(.))) %>%
                 mutate(id_j = as.numeric(as.factor(paste0(COUNTRY, JKZONES, IDSCHOOL)))) %>%
                 mutate(id_s = as.numeric(as.factor(paste0(COUNTRY, JKZONES)))) %>%
                 mutate(id_r = as.numeric(as.factor(paste0(COUNTRY, JKZONES, JKREPS)))) %>%
                 mutate(id_k = as.numeric(as.factor(paste0(COUNTRY)))) %>%
                 # survey weights
                 mutate(wt = TOTWGTS) %>%
                 # students weights
                 mutate(wi = WGTFAC2S*WGTADJ2S*WGTADJ3S) %>%
                 # school weights
                 mutate(wj = WGTFAC1*WGTADJ1S) %>%
                 # create senate weights
                 r4sda::senate_weights(., wt = 'wt', id_k = 'id_k', scale = 1000) %>%
                 # create scaled weights
                 r4sda::lsa_weights(., 
                   id_i = 'id_i', 
                   id_j = 'id_j', 
                   id_k = 'id_k', 
                   wt = 'wt', 
                   wi = 'wi', 
                   wj = 'wj') %>%
                 dplyr::glimpse()

# -----------------------------------------------
# check clustering assumptions
# -----------------------------------------------

# strata are unique across countries
data_model_09 %>%
r4sda::check_cluster_id(cluster_1 = 'id_s', cluster_2 = 'id_k')

# schools are unique across countries
data_model_09 %>%
r4sda::check_cluster_id(cluster_1 = 'id_j', cluster_2 = 'id_k')

# schools are unique across strata
data_model_09 %>%
r4sda::check_cluster_id(cluster_1 = 'id_j', cluster_2 = 'id_s')

# psu are unique across countries
data_model_09 %>%
r4sda::check_cluster_id(cluster_1 = 'id_r', cluster_2 = 'id_k')

# psu are unique across strata
data_model_09 %>%
r4sda::check_cluster_id(cluster_1 = 'id_r', cluster_2 = 'id_s')

# -----------------------------------------------
# load data
# -----------------------------------------------

data_16 <- readRDS(paste0(data_folder, 'iccs_2016_stu_int.rds'))

# -----------------------------------------------
# generic survey design variables
# -----------------------------------------------

library(dplyr)
data_model_16 <- data_16 %>%
                 # remove labels
                 r4sda::remove_labels() %>%
                 # clustering
                 mutate(id_i = seq(1:nrow(.))) %>%
                 mutate(id_j = as.numeric(as.factor(paste0(COUNTRY, JKZONES, IDSCHOOL)))) %>%
                 mutate(id_s = as.numeric(as.factor(paste0(COUNTRY, JKZONES)))) %>%
                 mutate(id_r = as.numeric(as.factor(paste0(COUNTRY, JKZONES, JKREPS)))) %>%
                 mutate(id_k = as.numeric(as.factor(paste0(COUNTRY)))) %>%
                 # survey weights
                 mutate(wt = TOTWGTS) %>%
                 # students weights
                 mutate(wi = WGTFAC2S*WGTADJ2S*WGTADJ3S) %>%
                 # school weights
                 mutate(wj = WGTFAC1*WGTADJ1S) %>%
                 # create senate weights
                 r4sda::senate_weights(., wt = 'wt', id_k = 'id_k', scale = 1000) %>%
                 # create scaled weights
                 r4sda::lsa_weights(., 
                   id_i = 'id_i', 
                   id_j = 'id_j', 
                   id_k = 'id_k', 
                   wt = 'wt', 
                   wi = 'wi', 
                   wj = 'wj') %>%
                 dplyr::glimpse()

# -----------------------------------------------
# check clustering assumptions
# -----------------------------------------------

# strata are unique across countries
data_model_16 %>%
r4sda::check_cluster_id(cluster_1 = 'id_s', cluster_2 = 'id_k')

# schools are unique across countries
data_model_16 %>%
r4sda::check_cluster_id(cluster_1 = 'id_j', cluster_2 = 'id_k')

# schools are unique across strata
data_model_16 %>%
r4sda::check_cluster_id(cluster_1 = 'id_j', cluster_2 = 'id_s')

# psu are unique across countries
data_model_16 %>%
r4sda::check_cluster_id(cluster_1 = 'id_r', cluster_2 = 'id_k')

# psu are unique across strata
data_model_16 %>%
r4sda::check_cluster_id(cluster_1 = 'id_r', cluster_2 = 'id_s')

```


# Problem 4: entried values may obstacle interpretation

- In most scenarios in ILSA, data entry values for response alternatives are asigned from left to right.
- Thus, conditional to the defined response alternatives order, if these values can be interpreted in attribute-like direction.
- That is, if higher values always express higher agreement, higher endorsement, higher frequency, or else.
- For the current illustration, we will recode the response values from Question 22 in ICCS 2016, the scale "What is good for democracy" (see Quaranta, 2019).

## Code 04: compute variables

- The following code first documents the item we will recode
- Then, it rename the selected variable with a defined list of names
- Afterwards, these values are recoded according to an interpretable scheme
  + This interpretable scheme follows the Complex class response pattern from Quaranta (2019)
- Finally, the recoded data frame is joined to the rest of the data
- All new variables are assigned labels, so we can read later on what are these variables
- A `data_model` data frame is save for later use


```{r, echo=TRUE}

# -----------------------------------------------------------------------------
# computes
# -----------------------------------------------------------------------------


# ---------------------------------------- 
# data for 2009
# ---------------------------------------- 

opd_09 <- data_model_09 %>%
              # socioeconomic status
              mutate(ses = r4sda::z_score(NISB)) %>%              # mean z score
              mutate(ses_c = r4sda::c_mean(ses, id_j)) %>%        # means by clusters
              mutate(ses_g = r4sda::c_wmean(ses, ws, id_k))  %>%  # grand mean
              mutate(ses_m = ses - ses_g   )     %>%  # cgm
              mutate(ses_w = ses - ses_c   )     %>%  # cwc
              mutate(ses_b = ses_c - ses_g )     %>%  # centered school means
              # open classroom discussion
              ## opd scores in international scale
              mutate(opd = (OPDISC-50)/10)                   %>% 
              mutate(opd_c = r4sda::c_mean(opd, id_j))       %>%  # means by clusters
              mutate(opd_g = r4sda::c_wmean(opd, ws, id_k))  %>%  # grand mean
              mutate(opd_m = opd - opd_g   )     %>%  # cgm
              mutate(opd_w = opd - opd_c   )     %>%  # within centering
              mutate(opd_b = opd_c - opd_g )     %>%  # between centerin
              glimpse()


# ---------------------------------------- 
# data for 2016
# ---------------------------------------- 

opd_16 <- data_model_16 %>%
              # socioeconomic status
              mutate(ses = r4sda::z_score(S_NISB)) %>%            # mean z score
              mutate(ses_c = r4sda::c_mean(ses, id_j)) %>%        # means by clusters
              mutate(ses_g = r4sda::c_wmean(ses, ws, id_k))  %>%  # grand mean
              mutate(ses_m = ses - ses_g   )     %>%  # cgm
              mutate(ses_w = ses - ses_c   )     %>%  # cwc
              mutate(ses_b = ses_c - ses_g )     %>%  # centered school means
              # open classroom discussion
              ## opd scores in international scale
              mutate(opd = (S_OPDISC-50)/10)                 %>% 
              mutate(opd_c = r4sda::c_mean(opd, id_j))       %>% # means by clusters
              mutate(opd_g = r4sda::c_wmean(opd, ws, id_k))  %>% # grand mean
              mutate(opd_m = opd - opd_g   )     %>%  # cgm
              mutate(opd_w = opd - opd_c   )     %>%  # within centering
              mutate(opd_b = opd_c - opd_g )     %>%  # between centerin
              glimpse()


```

# Problem 5: save data for modelling

- With all the previous code, we now have a data frame that can be modelled in the way we desired. However, is not in the format that other sofwate we may need.

- The following lines of code can help users to export the prepared data to other statistical packages including: STATA, MPLUS, and Latent Gold.

- With the exported data, now we are ready for modelling!

- In the current approach we wil just save the "`*.rds`" files, we will create individual files for modelling with mplus in the next code file.

## Save data to RDS

```{r, echo=TRUE}

# -----------------------------------------------------------------------------
# save data to RDS
# -----------------------------------------------------------------------------


# -----------------------------------------------
# add missing variable labels
# -----------------------------------------------

opd_09 <- opd_09 %>%
labelled::copy_labels(data_09, .) %>%
labelled::set_variable_labels(id_k = 'unique country id') %>%
labelled::set_variable_labels(id_s = 'unique strata id') %>%
labelled::set_variable_labels(id_r = 'unique psu id') %>%
labelled::set_variable_labels(id_j = 'unique school id') %>%
labelled::set_variable_labels(id_i = 'unique student id') %>%
labelled::set_variable_labels(wt  = 'weight, total weight for students') %>%
labelled::set_variable_labels(wi  = 'weight, within schools') %>%
labelled::set_variable_labels(wj  = 'weight, between schools') %>%
labelled::set_variable_labels(wa1 = 'weight, within schools, normalized weights (method 2)') %>%
labelled::set_variable_labels(wa2 = 'weight, between schools, normalized weights (method 2)') %>%
labelled::set_variable_labels(wb1 = 'weight, within schools, effective sample size weights (method 1)') %>%
labelled::set_variable_labels(wb2 = 'weight, between schools, effective sample size weights (method 1)') %>%
labelled::set_variable_labels(ws  = 'weight, senate weight up to 1000 cases')

# -----------------------------------------------
# save variables table
# -----------------------------------------------

opd_09 %>%
r4sda::variables_table() %>%
openxlsx::write.xlsx(., paste0(data_folder,'data_opd_09_codebook.xlsx'))

# -----------------------------------------------
# save
# -----------------------------------------------

saveRDS(opd_09, paste0(data_folder,'data_opd_09.rds'))

# -----------------------------------------------
# add missing variable labels
# -----------------------------------------------

opd_16 <- opd_16 %>%
labelled::copy_labels(data_16, .) %>%
labelled::set_variable_labels(id_k = 'unique country id') %>%
labelled::set_variable_labels(id_s = 'unique strata id') %>%
labelled::set_variable_labels(id_r = 'unique psu id') %>%
labelled::set_variable_labels(id_j = 'unique school id') %>%
labelled::set_variable_labels(id_i = 'unique student id') %>%
labelled::set_variable_labels(wt  = 'weight, total weight for students') %>%
labelled::set_variable_labels(wi  = 'weight, within schools') %>%
labelled::set_variable_labels(wj  = 'weight, between schools') %>%
labelled::set_variable_labels(wa1 = 'weight, within schools, normalized weights (method 2)') %>%
labelled::set_variable_labels(wa2 = 'weight, between schools, normalized weights (method 2)') %>%
labelled::set_variable_labels(wb1 = 'weight, within schools, effective sample size weights (method 1)') %>%
labelled::set_variable_labels(wb2 = 'weight, between schools, effective sample size weights (method 1)') %>%
labelled::set_variable_labels(ws  = 'weight, senate weight up to 1000 cases')

# -----------------------------------------------
# save variables table
# -----------------------------------------------

opd_16 %>%
r4sda::variables_table() %>%
openxlsx::write.xlsx(., paste0(data_folder,'data_opd_16_codebook.xlsx'))

# -----------------------------------------------
# save
# -----------------------------------------------

saveRDS(opd_16, paste0(data_folder,'data_opd_16.rds'))

```


# Estimated times

```{r , echo=FALSE, include=FALSE}

# ---------------------------------------- 
# estimated times
# ---------------------------------------- 

# get current time
end_time <- Sys.time()

# create table
time_table <- data.frame(
  events = c('start', 'end'),
  times = c(start_time, end_time)
  )

# display time
knitr::kable(time_table, align = 'r') 

```



```{r , echo=TRUE}

# ---------------------------------------- 
# estimated times
# ---------------------------------------- 

difftime(end_time, start_time, units="mins")


```


