---
title: "Code 3: fit models"
subtitle: "CIES 2021: not everyone has the chance"
author: "dacarras"
date: 'April 29th, 2021'
output:
  html_document:
    theme: paper
    highlight: kate
    number_sections: true
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    fig_width: 10 
    fig_height: 8 
---


<style>
  .main-container {
    max-width: 1600px !important;
  }
  .list-group-item.active, 
  .list-group-item.active:focus, 
  .list-group-item.active:hover {
    background-color: #373334;
  }
</style>



```{r setup, include=FALSE}
#------------------------------------------------------------------------------
# setup
#------------------------------------------------------------------------------

# knitr option
knitr::opts_chunk$set(dev = 'png')
options(knitr.kable.NA = '', digits = 2)

# set appropiate time zone via OlsonNames()
Sys.setenv(TZ="America/Santiago")
Sys.getenv("TZ")
Sys.time()

# fonts
Sys.setenv(LANG="en_US.UTF-8")

# load main library
library(dplyr)


# ---------------------------------------------------------
# get times
# ---------------------------------------------------------

start_time <- Sys.time()

```


# Libraries

## What libraries are used in the present code

```{r , echo=TRUE, warning=FALSE, eval = FALSE}

#------------------------------------------------------------------------------
# libraries
#------------------------------------------------------------------------------

# ---------------------------------------------------------
# libraries for this code
# ---------------------------------------------------------

install.packages('tidyverse')
# many libraries for data management

install.packages('haven')     
# library to open SPSS, STATA, and SAS files

install.packages('labelled')     
# library to add variable labels to data frames

install.packages('devtools')  
# to install developmental libraries

install.packages('MplusAutomation')     
# library to fit model in MPLUS from R

devtools::install_github("dacarras/r4sda") 
# experimental library for analysis of secondary data

```



# File Locations

## Folders

```{r , echo=TRUE, warning=FALSE}

#------------------------------------------------------------------------------
# folders
#------------------------------------------------------------------------------

# ---------------------------------------------------------
# get local path from relative path
# ---------------------------------------------------------

local_path <- function(x){
paste0(tools::file_path_as_absolute('..'),x)  
}

# Note: set current directory as working directory
#       e.g. `setwd("/Users/d/cies_2021_opd/01_syntax/")`
#       When a rmd file is run in Rstudio, current directory
#       is the working directory.


# ---------------------------------------------------------
# relative position of folders
# ---------------------------------------------------------

# 00_data
# 01_syntax
# 02_mplus
# 03_figures

# ---------------------------------------------------------
# folder with data files
# ---------------------------------------------------------

data_folder      <- local_path('/00_data/')
syntax_folder    <- local_path('/01_syntax/')
plot_folder      <- local_path('/02_figures/')

# ---------------------------------------------------------
# load main library
# ---------------------------------------------------------

library(dplyr)

# ---------------------------------------------------------
# check folder
# ---------------------------------------------------------

list.files(data_folder)

```

## Load files

```{r , echo=TRUE}

#------------------------------------------------------------------------------
# load data
#------------------------------------------------------------------------------

# ---------------------------------------------------------
# files
# ---------------------------------------------------------

opd_09 <- readRDS(paste0(data_folder, 'data_opd_09.rds')) %>%
             r4sda::remove_labels()

opd_16 <- readRDS(paste0(data_folder, 'data_opd_16.rds')) %>%
             r4sda::remove_labels()

# ----------------------------------------------- 
# data frame dimensions
# -----------------------------------------------

data.frame(
  data = c('iccs 2009', 'iccs 2016'),
  rows = c(nrow(opd_09), nrow(opd_16)),
  columns = c(ncol(opd_09), ncol(opd_16))
  ) %>%
knitr::kable(., digits = 2)


# ----------------------------------------------- 
# main library
# -----------------------------------------------

library(dplyr)

```


# General Mplus model

## Data per country

```{r , echo=TRUE}

#---------------------------------------------------------------------------------------------------------
# data per country
#---------------------------------------------------------------------------------------------------------

# ---------------------------------------- 
# country table date 2009
# ---------------------------------------- 

dplyr::count(opd_09, IDCNTRY, COUNTRY) %>%
knitr::kable(., format = 'markdown')

# ---------------------------------------- 
# data for 2009
# ---------------------------------------- 

opd_09_AUT <- dplyr::filter(opd_09, COUNTRY == 'AUT')
opd_09_BGR <- dplyr::filter(opd_09, COUNTRY == 'BGR')
opd_09_CHL <- dplyr::filter(opd_09, COUNTRY == 'CHL')
opd_09_TWN <- dplyr::filter(opd_09, COUNTRY == 'TWN')
opd_09_COL <- dplyr::filter(opd_09, COUNTRY == 'COL')
opd_09_CYP <- dplyr::filter(opd_09, COUNTRY == 'CYP')
opd_09_CZE <- dplyr::filter(opd_09, COUNTRY == 'CZE')
opd_09_DNK <- dplyr::filter(opd_09, COUNTRY == 'DNK')
opd_09_DOM <- dplyr::filter(opd_09, COUNTRY == 'DOM')
opd_09_EST <- dplyr::filter(opd_09, COUNTRY == 'EST')
opd_09_FIN <- dplyr::filter(opd_09, COUNTRY == 'FIN')
opd_09_GRC <- dplyr::filter(opd_09, COUNTRY == 'GRC')
opd_09_GTM <- dplyr::filter(opd_09, COUNTRY == 'GTM')
opd_09_HKG <- dplyr::filter(opd_09, COUNTRY == 'HKG')
opd_09_IDN <- dplyr::filter(opd_09, COUNTRY == 'IDN')
opd_09_IRL <- dplyr::filter(opd_09, COUNTRY == 'IRL')
opd_09_ITA <- dplyr::filter(opd_09, COUNTRY == 'ITA')
opd_09_KOR <- dplyr::filter(opd_09, COUNTRY == 'KOR')
opd_09_LVA <- dplyr::filter(opd_09, COUNTRY == 'LVA')
opd_09_LIE <- dplyr::filter(opd_09, COUNTRY == 'LIE')

# Note: LTU, LUX and MLT fitted models do not work well, due to having to few schools.
#       Thus, are excluded from the present exercise.

# opd_09_LTU <- dplyr::filter(opd_09, COUNTRY == 'LTU')
# opd_09_LUX <- dplyr::filter(opd_09, COUNTRY == 'LUX')
# opd_09_MLT <- dplyr::filter(opd_09, COUNTRY == 'MLT')

opd_09_MEX <- dplyr::filter(opd_09, COUNTRY == 'MEX')
opd_09_NLD <- dplyr::filter(opd_09, COUNTRY == 'NLD')
opd_09_NZL <- dplyr::filter(opd_09, COUNTRY == 'NZL')
opd_09_NOR <- dplyr::filter(opd_09, COUNTRY == 'NOR')
opd_09_PRY <- dplyr::filter(opd_09, COUNTRY == 'PRY')
opd_09_POL <- dplyr::filter(opd_09, COUNTRY == 'POL')
opd_09_RUS <- dplyr::filter(opd_09, COUNTRY == 'RUS')
opd_09_SVK <- dplyr::filter(opd_09, COUNTRY == 'SVK')
opd_09_SVN <- dplyr::filter(opd_09, COUNTRY == 'SVN')
opd_09_ESP <- dplyr::filter(opd_09, COUNTRY == 'ESP')
opd_09_SWE <- dplyr::filter(opd_09, COUNTRY == 'SWE')
opd_09_CHE <- dplyr::filter(opd_09, COUNTRY == 'CHE')
opd_09_THA <- dplyr::filter(opd_09, COUNTRY == 'THA')
opd_09_ENG <- dplyr::filter(opd_09, COUNTRY == 'ENG')
opd_09_BFL <- dplyr::filter(opd_09, COUNTRY == 'BFL')


# ---------------------------------------- 
# country table date 2009
# ---------------------------------------- 

dplyr::count(opd_16, IDCNTRY, COUNTRY) %>%
knitr::kable(., format = 'markdown')

# ---------------------------------------- 
# data for 2016
# ---------------------------------------- 

opd_16_BGR <- dplyr::filter(opd_16, COUNTRY == 'BGR')
opd_16_CHL <- dplyr::filter(opd_16, COUNTRY == 'CHL')
opd_16_TWN <- dplyr::filter(opd_16, COUNTRY == 'TWN')
opd_16_COL <- dplyr::filter(opd_16, COUNTRY == 'COL')
opd_16_HRV <- dplyr::filter(opd_16, COUNTRY == 'HRV')
opd_16_DNK <- dplyr::filter(opd_16, COUNTRY == 'DNK')
opd_16_DOM <- dplyr::filter(opd_16, COUNTRY == 'DOM')
opd_16_EST <- dplyr::filter(opd_16, COUNTRY == 'EST')
opd_16_FIN <- dplyr::filter(opd_16, COUNTRY == 'FIN')
opd_16_HKG <- dplyr::filter(opd_16, COUNTRY == 'HKG')
opd_16_ITA <- dplyr::filter(opd_16, COUNTRY == 'ITA')
opd_16_KOR <- dplyr::filter(opd_16, COUNTRY == 'KOR')
opd_16_LVA <- dplyr::filter(opd_16, COUNTRY == 'LVA')
opd_16_LTU <- dplyr::filter(opd_16, COUNTRY == 'LTU')
opd_16_MLT <- dplyr::filter(opd_16, COUNTRY == 'MLT')
opd_16_MEX <- dplyr::filter(opd_16, COUNTRY == 'MEX')
opd_16_NLD <- dplyr::filter(opd_16, COUNTRY == 'NLD')
opd_16_NOR <- dplyr::filter(opd_16, COUNTRY == 'NOR')
opd_16_PER <- dplyr::filter(opd_16, COUNTRY == 'PER')
opd_16_RUS <- dplyr::filter(opd_16, COUNTRY == 'RUS')
opd_16_SVN <- dplyr::filter(opd_16, COUNTRY == 'SVN')
opd_16_SWE <- dplyr::filter(opd_16, COUNTRY == 'SWE')
opd_16_BFL <- dplyr::filter(opd_16, COUNTRY == 'BFL')
opd_16_DNW <- dplyr::filter(opd_16, COUNTRY == 'DNW')


```


## Example model

- This model is not for interpretation.
- We use Chile 2009, because we know it present large oportunity gap.

```{r , echo=TRUE}

#---------------------------------------------------------------------------------------------------------
# specify model
#---------------------------------------------------------------------------------------------------------

library(MplusAutomation)
oportunity_gap_model <- mplusObject(
MODEL = '

%WITHIN% 
opd on ses_w (w);


%BETWEEN%
opd on ses_b (b);

',
ANALYSIS = '
TYPE = TWOLEVEL COMPLEX;
ESTIMATOR = MLR;
',

VARIABLE = '
! variables with restricted variance
WITHIN  = ses_w;
BETWEEN = ses_b;

!complex sample design
STRATIFICATION = id_s;
CLUSTER = id_j;

!multilevel specification
WEIGHT  = wi;
BWEIGHT = wj;
WTSCALE = ECLUSTER;
BWTSCALE = SAMPLE;

USEVARIABLES =
opd
ses_w
ses_b
;
',
MODELCONSTRAINT =
'
new (
ce_w
ce_b
ce_c
);

!contextual effect of ses
ce_w = w;
ce_b = b;
ce_c = b - w;
',
OUTPUT ='
STAND
TECH1
TECH3
SAMPSTAT
CINTERVAL
;
',
rdata = opd_09_CHL)


# ---------------------------------------- 
# fit models
# ---------------------------------------- 

fit_gap <- mplusModeler(oportunity_gap_model,
              hashfilename = FALSE, 
              modelout = 'fit_09_CHL.inp',
              writeData = 'always', 
              run = 1L)

# ---------------------------------------- 
# compare estimates
# ---------------------------------------- 


texreg::screenreg(list(fit_gap), 
    type = 'un',
    star.symbol = "\\*", 
    center = TRUE, 
    doctype = FALSE,
    dcolumn = TRUE, 
    booktabs = TRUE,
    single.row=TRUE,
    summaries = c("Observations"))


```

## Models by country 2009

```{r , echo=TRUE}

#---------------------------------------------------------------------------------------------------------
# fit models 2009
#---------------------------------------------------------------------------------------------------------

# ---------------------------------------- 
# update models
# ---------------------------------------- 

library(MplusAutomation)

gap_09_AUT <- update(fit_gap, rdata = opd_09_AUT)
gap_09_BGR <- update(fit_gap, rdata = opd_09_BGR)
gap_09_CHL <- update(fit_gap, rdata = opd_09_CHL)
gap_09_TWN <- update(fit_gap, rdata = opd_09_TWN)
gap_09_COL <- update(fit_gap, rdata = opd_09_COL)
gap_09_CYP <- update(fit_gap, rdata = opd_09_CYP)
gap_09_CZE <- update(fit_gap, rdata = opd_09_CZE)
gap_09_DNK <- update(fit_gap, rdata = opd_09_DNK)
gap_09_DOM <- update(fit_gap, rdata = opd_09_DOM)
gap_09_EST <- update(fit_gap, rdata = opd_09_EST)
gap_09_FIN <- update(fit_gap, rdata = opd_09_FIN)
gap_09_GRC <- update(fit_gap, rdata = opd_09_GRC)
gap_09_GTM <- update(fit_gap, rdata = opd_09_GTM)
gap_09_HKG <- update(fit_gap, rdata = opd_09_HKG)
gap_09_IDN <- update(fit_gap, rdata = opd_09_IDN)
gap_09_IRL <- update(fit_gap, rdata = opd_09_IRL)
gap_09_ITA <- update(fit_gap, rdata = opd_09_ITA)
gap_09_KOR <- update(fit_gap, rdata = opd_09_KOR)
gap_09_LVA <- update(fit_gap, rdata = opd_09_LVA)
gap_09_LIE <- update(fit_gap, rdata = opd_09_LIE)
# gap_09_LTU <- update(fit_gap, rdata = opd_09_LTU)
# gap_09_LUX <- update(fit_gap, rdata = opd_09_LUX)
# gap_09_MLT <- update(fit_gap, rdata = opd_09_MLT)
gap_09_MEX <- update(fit_gap, rdata = opd_09_MEX)
gap_09_NLD <- update(fit_gap, rdata = opd_09_NLD)
gap_09_NZL <- update(fit_gap, rdata = opd_09_NZL)
gap_09_NOR <- update(fit_gap, rdata = opd_09_NOR)
gap_09_PRY <- update(fit_gap, rdata = opd_09_PRY)
gap_09_POL <- update(fit_gap, rdata = opd_09_POL)
gap_09_RUS <- update(fit_gap, rdata = opd_09_RUS)
gap_09_SVK <- update(fit_gap, rdata = opd_09_SVK)
gap_09_SVN <- update(fit_gap, rdata = opd_09_SVN)
gap_09_ESP <- update(fit_gap, rdata = opd_09_ESP)
gap_09_SWE <- update(fit_gap, rdata = opd_09_SWE)
gap_09_CHE <- update(fit_gap, rdata = opd_09_CHE)
gap_09_THA <- update(fit_gap, rdata = opd_09_THA)
gap_09_ENG <- update(fit_gap, rdata = opd_09_ENG)
gap_09_BFL <- update(fit_gap, rdata = opd_09_BFL)

# ---------------------------------------- 
# fit models
# ---------------------------------------- 

fit_09_AUT <- mplusModeler(gap_09_AUT, modelout = 'fit_09_AUT.inp', run = 1L, hashfilename = FALSE)
fit_09_BGR <- mplusModeler(gap_09_BGR, modelout = 'fit_09_BGR.inp', run = 1L, hashfilename = FALSE)
fit_09_CHL <- mplusModeler(gap_09_CHL, modelout = 'fit_09_CHL.inp', run = 1L, hashfilename = FALSE)
fit_09_TWN <- mplusModeler(gap_09_TWN, modelout = 'fit_09_TWN.inp', run = 1L, hashfilename = FALSE)
fit_09_COL <- mplusModeler(gap_09_COL, modelout = 'fit_09_COL.inp', run = 1L, hashfilename = FALSE)
fit_09_CYP <- mplusModeler(gap_09_CYP, modelout = 'fit_09_CYP.inp', run = 1L, hashfilename = FALSE)
fit_09_CZE <- mplusModeler(gap_09_CZE, modelout = 'fit_09_CZE.inp', run = 1L, hashfilename = FALSE)
fit_09_DNK <- mplusModeler(gap_09_DNK, modelout = 'fit_09_DNK.inp', run = 1L, hashfilename = FALSE)
fit_09_DOM <- mplusModeler(gap_09_DOM, modelout = 'fit_09_DOM.inp', run = 1L, hashfilename = FALSE)
fit_09_EST <- mplusModeler(gap_09_EST, modelout = 'fit_09_EST.inp', run = 1L, hashfilename = FALSE)
fit_09_FIN <- mplusModeler(gap_09_FIN, modelout = 'fit_09_FIN.inp', run = 1L, hashfilename = FALSE)
fit_09_GRC <- mplusModeler(gap_09_GRC, modelout = 'fit_09_GRC.inp', run = 1L, hashfilename = FALSE)
fit_09_GTM <- mplusModeler(gap_09_GTM, modelout = 'fit_09_GTM.inp', run = 1L, hashfilename = FALSE)
fit_09_HKG <- mplusModeler(gap_09_HKG, modelout = 'fit_09_HKG.inp', run = 1L, hashfilename = FALSE)
fit_09_IDN <- mplusModeler(gap_09_IDN, modelout = 'fit_09_IDN.inp', run = 1L, hashfilename = FALSE)
fit_09_IRL <- mplusModeler(gap_09_IRL, modelout = 'fit_09_IRL.inp', run = 1L, hashfilename = FALSE)
fit_09_ITA <- mplusModeler(gap_09_ITA, modelout = 'fit_09_ITA.inp', run = 1L, hashfilename = FALSE)
fit_09_KOR <- mplusModeler(gap_09_KOR, modelout = 'fit_09_KOR.inp', run = 1L, hashfilename = FALSE)
fit_09_LVA <- mplusModeler(gap_09_LVA, modelout = 'fit_09_LVA.inp', run = 1L, hashfilename = FALSE)
fit_09_LIE <- mplusModeler(gap_09_LIE, modelout = 'fit_09_LIE.inp', run = 1L, hashfilename = FALSE)

# Note: LTU, LUX and MLT fitted models do not work well, due to having to few schools.
#       Thus, are excluded from the present exercise.
# fit_09_LTU <- mplusModeler(gap_09_LTU, modelout = 'fit_09_LTU.inp', run = 1L, hashfilename = FALSE)
# fit_09_LUX <- mplusModeler(gap_09_LUX, modelout = 'fit_09_LUX.inp', run = 1L, hashfilename = FALSE)
# fit_09_MLT <- mplusModeler(gap_09_MLT, modelout = 'fit_09_MLT.inp', run = 1L, hashfilename = FALSE)

fit_09_MEX <- mplusModeler(gap_09_MEX, modelout = 'fit_09_MEX.inp', run = 1L, hashfilename = FALSE)
fit_09_NLD <- mplusModeler(gap_09_NLD, modelout = 'fit_09_NLD.inp', run = 1L, hashfilename = FALSE)
fit_09_NZL <- mplusModeler(gap_09_NZL, modelout = 'fit_09_NZL.inp', run = 1L, hashfilename = FALSE)
fit_09_NOR <- mplusModeler(gap_09_NOR, modelout = 'fit_09_NOR.inp', run = 1L, hashfilename = FALSE)
fit_09_PRY <- mplusModeler(gap_09_PRY, modelout = 'fit_09_PRY.inp', run = 1L, hashfilename = FALSE)
fit_09_POL <- mplusModeler(gap_09_POL, modelout = 'fit_09_POL.inp', run = 1L, hashfilename = FALSE)
fit_09_RUS <- mplusModeler(gap_09_RUS, modelout = 'fit_09_RUS.inp', run = 1L, hashfilename = FALSE)
fit_09_SVK <- mplusModeler(gap_09_SVK, modelout = 'fit_09_SVK.inp', run = 1L, hashfilename = FALSE)
fit_09_SVN <- mplusModeler(gap_09_SVN, modelout = 'fit_09_SVN.inp', run = 1L, hashfilename = FALSE)
fit_09_ESP <- mplusModeler(gap_09_ESP, modelout = 'fit_09_ESP.inp', run = 1L, hashfilename = FALSE)
fit_09_SWE <- mplusModeler(gap_09_SWE, modelout = 'fit_09_SWE.inp', run = 1L, hashfilename = FALSE)
fit_09_CHE <- mplusModeler(gap_09_CHE, modelout = 'fit_09_CHE.inp', run = 1L, hashfilename = FALSE)
fit_09_THA <- mplusModeler(gap_09_THA, modelout = 'fit_09_THA.inp', run = 1L, hashfilename = FALSE)
fit_09_ENG <- mplusModeler(gap_09_ENG, modelout = 'fit_09_ENG.inp', run = 1L, hashfilename = FALSE)
fit_09_BFL <- mplusModeler(gap_09_BFL, modelout = 'fit_09_BFL.inp', run = 1L, hashfilename = FALSE)

```



## Models by country 2016

```{r , echo=TRUE}

#---------------------------------------------------------------------------------------------------------
# fit models 2016
#---------------------------------------------------------------------------------------------------------

# ---------------------------------------- 
# update models
# ---------------------------------------- 

gap_16_BGR <- update(fit_gap, rdata = opd_16_BGR)
gap_16_CHL <- update(fit_gap, rdata = opd_16_CHL)
gap_16_TWN <- update(fit_gap, rdata = opd_16_TWN)
gap_16_COL <- update(fit_gap, rdata = opd_16_COL)
gap_16_HRV <- update(fit_gap, rdata = opd_16_HRV)
gap_16_DNK <- update(fit_gap, rdata = opd_16_DNK)
gap_16_DOM <- update(fit_gap, rdata = opd_16_DOM)
gap_16_EST <- update(fit_gap, rdata = opd_16_EST)
gap_16_FIN <- update(fit_gap, rdata = opd_16_FIN)
gap_16_HKG <- update(fit_gap, rdata = opd_16_HKG)
gap_16_ITA <- update(fit_gap, rdata = opd_16_ITA)
gap_16_KOR <- update(fit_gap, rdata = opd_16_KOR)
gap_16_LVA <- update(fit_gap, rdata = opd_16_LVA)
gap_16_LTU <- update(fit_gap, rdata = opd_16_LTU)
gap_16_MLT <- update(fit_gap, rdata = opd_16_MLT)
gap_16_MEX <- update(fit_gap, rdata = opd_16_MEX)
gap_16_NLD <- update(fit_gap, rdata = opd_16_NLD)
gap_16_NOR <- update(fit_gap, rdata = opd_16_NOR)
gap_16_PER <- update(fit_gap, rdata = opd_16_PER)
gap_16_RUS <- update(fit_gap, rdata = opd_16_RUS)
gap_16_SVN <- update(fit_gap, rdata = opd_16_SVN)
gap_16_SWE <- update(fit_gap, rdata = opd_16_SWE)
gap_16_BFL <- update(fit_gap, rdata = opd_16_BFL)
gap_16_DNW <- update(fit_gap, rdata = opd_16_DNW)

# ---------------------------------------- 
# fit models
# ---------------------------------------- 

fit_16_BGR <- mplusModeler(gap_16_BGR, modelout = 'fit_16_BGR.inp', run = 1L, hashfilename = FALSE)
fit_16_CHL <- mplusModeler(gap_16_CHL, modelout = 'fit_16_CHL.inp', run = 1L, hashfilename = FALSE)
fit_16_TWN <- mplusModeler(gap_16_TWN, modelout = 'fit_16_TWN.inp', run = 1L, hashfilename = FALSE)
fit_16_COL <- mplusModeler(gap_16_COL, modelout = 'fit_16_COL.inp', run = 1L, hashfilename = FALSE)
fit_16_HRV <- mplusModeler(gap_16_HRV, modelout = 'fit_16_HRV.inp', run = 1L, hashfilename = FALSE)
fit_16_DNK <- mplusModeler(gap_16_DNK, modelout = 'fit_16_DNK.inp', run = 1L, hashfilename = FALSE)
fit_16_DOM <- mplusModeler(gap_16_DOM, modelout = 'fit_16_DOM.inp', run = 1L, hashfilename = FALSE)
fit_16_EST <- mplusModeler(gap_16_EST, modelout = 'fit_16_EST.inp', run = 1L, hashfilename = FALSE)
fit_16_FIN <- mplusModeler(gap_16_FIN, modelout = 'fit_16_FIN.inp', run = 1L, hashfilename = FALSE)
fit_16_HKG <- mplusModeler(gap_16_HKG, modelout = 'fit_16_HKG.inp', run = 1L, hashfilename = FALSE)
fit_16_ITA <- mplusModeler(gap_16_ITA, modelout = 'fit_16_ITA.inp', run = 1L, hashfilename = FALSE)
fit_16_KOR <- mplusModeler(gap_16_KOR, modelout = 'fit_16_KOR.inp', run = 1L, hashfilename = FALSE)
fit_16_LVA <- mplusModeler(gap_16_LVA, modelout = 'fit_16_LVA.inp', run = 1L, hashfilename = FALSE)
fit_16_LTU <- mplusModeler(gap_16_LTU, modelout = 'fit_16_LTU.inp', run = 1L, hashfilename = FALSE)
fit_16_MLT <- mplusModeler(gap_16_MLT, modelout = 'fit_16_MLT.inp', run = 1L, hashfilename = FALSE)
fit_16_MEX <- mplusModeler(gap_16_MEX, modelout = 'fit_16_MEX.inp', run = 1L, hashfilename = FALSE)
fit_16_NLD <- mplusModeler(gap_16_NLD, modelout = 'fit_16_NLD.inp', run = 1L, hashfilename = FALSE)
fit_16_NOR <- mplusModeler(gap_16_NOR, modelout = 'fit_16_NOR.inp', run = 1L, hashfilename = FALSE)
fit_16_PER <- mplusModeler(gap_16_PER, modelout = 'fit_16_PER.inp', run = 1L, hashfilename = FALSE)
fit_16_RUS <- mplusModeler(gap_16_RUS, modelout = 'fit_16_RUS.inp', run = 1L, hashfilename = FALSE)
fit_16_SVN <- mplusModeler(gap_16_SVN, modelout = 'fit_16_SVN.inp', run = 1L, hashfilename = FALSE)
fit_16_SWE <- mplusModeler(gap_16_SWE, modelout = 'fit_16_SWE.inp', run = 1L, hashfilename = FALSE)
fit_16_BFL <- mplusModeler(gap_16_BFL, modelout = 'fit_16_BFL.inp', run = 1L, hashfilename = FALSE)
fit_16_DNW <- mplusModeler(gap_16_DNW, modelout = 'fit_16_DNW.inp', run = 1L, hashfilename = FALSE)


```


# Estimated times

```{r , echo=FALSE, include=FALSE}

# ---------------------------------------- 
# estimated times
# ---------------------------------------- 

# get current time
end_time <- Sys.time()

# create table
time_table <- data.frame(
  events = c('start', 'end'),
  times = c(start_time, end_time)
  )

```


```{r , echo=TRUE}

# ---------------------------------------- 
# starts and end times
# ---------------------------------------- 

# display time
knitr::kable(time_table, align = 'r') 


# ---------------------------------------- 
# estimated times in minutes
# ---------------------------------------- 

difftime(end_time, start_time, units="mins")

```



